The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-25 design.tex
rearrange the paper structure
start to design 6 experiments

\subsubsection{Master plan} % (fold)
\label{ssub:master_plam}
With the cloud manufacturing platform operating, demander comes, signs up and publish orders. Match module in platform informs the task messages in the order to every matched resources and services. After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before. Most of resource related decision making are well controlled by platform with the review module.

@@

Specifically, a simple instance with configuration \autoref{tab:simpleresourceconfiguration}--\ref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple resource configuration}
    \begin{tabular}{ccc}
    \toprule
    Resource & Type  & Capacity \\
    \midrule
    $r_1$ & 1     & 10 \\
    $r_2$ & 2     & 10 \\
    $r_3$ & 3     & 10 \\
    $r_4$ & 3     & 10 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simpleresourceconfiguration}%
\end{table}%
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources}
	\label{fig:scheduleChart}
\end{figure}
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period. Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.

@@

\begin{table}[!h]
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required and provided by $sc_l$ and $ms_l$ respectively, $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

@@

\begin{asparaenum}
\item Response for the task need $t_{ij}$($\tau\ge r_i$) with resource $mr_k$
\suspend{asparaenum}
\begin{numcases}{}
A_{k,\tau} \ge q_{\alpha,ij} &\\
P(mr_k) = \alpha &
\end{numcases}
If $mr_k$ meets the above condition, provider of it will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$. If $mr_k$ was finally chose, available of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$. The available will be return back after the finish of $t_{ij}$.
\resume{asparaenum}
\item Response for the service-call need $sc_l$($\tau\ge r_l$) with resume $mr_k$
\suspend{asparaenum}
\begin{numcases}{}
C_{k,\tau} > 0 & \\
P(mr_k) = \alpha
\end{numcases}
If $mr_k$ meets the above condition, provider($p_a$) of it will response the service-call need, the provider($p_b$) of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$, it's possible to let $p_a=p_b$. If $mr_k$ was finally chose, capacity of $mr_k$ will change as:
\begin{numcases}{}
C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\\
C_{k,\tau} := 0 & otherwise
\end{numcases}

Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed. Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
\begin{numcases}{}
\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
\end{numcases}
\resume{asparaenum}
\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$.
\end{asparaenum}
Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
\begin{numcases}{}
q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
\mathcal{A}_{ij} = \mathcal{B}_l
\end{numcases}

This condition is much same as service-call need $sc_l$ after the accomplishment frequent task $t_{ij}$:
\begin{numcases}{}
q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
\mathcal{A}_{ij} = \mathcal{A}_l
\end{numcases}
% subsection interactions_and_decisions (end)

@@

With the select decision of $t_{ij}$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
\begin{equation}
	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau},sc \text{ is service-call} \right\} \cup \mathcal{G}_{k,\tau}
\end{equation}
Then, the provider will add $t_{ij}$ to queue or process buffer according to:
\begin{numcases}{}
\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \\
\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
\end{numcases}

@@

With the select decision of $sc_l$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
\begin{equation}
	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{G}_{k,\tau}
\end{equation}
Then, the provider will add $sc_l$ to queue or process buffer according to:
\begin{numcases}{}
\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_l\} & if $\abs{\mathcal{L}_{k,\tau}\cup\mathcal{G}_{k,\tau}}=0$ \\
\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
\end{numcases}

@@

\begin{equation}
\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right)
\end{equation}
\begin{numcases}{\text{s.t.}}
L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\right\} & \\
f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\\
G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \\
f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \\
\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \\
f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$
\end{numcases}

Like the RCPSP

@@

We will ignore resource type subscript $\alpha$ here for the reason that resources perform the task already meet the type needs. With the assumption given above, higher resource occupation($p_{ij}\cdot q_{ij}$), lower delay($f_{ij} - p_{ij} - r_{ij}$), larger difference between actual and expected product quality($\delta_{ij}-\gamma_{ij}$), will turn out higher rank value($rank$) changing:
\begin{numcases}{}
rank := rank +
\frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} &\\
\delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
\end{numcases}

@@

This decision making is a control method for platform to keep the performance of tasks with content quality and efficiency. We denote the list of all resources with type $\alpha$ as $\bm{mr}_\alpha$ and the list of all services as $\bm{ms}$ at time $\tau$, after the sort these lists according to the scarcity and quality, the unqualified resources and services. Scarcity can be defined as:
\begin{numcases}{}
\sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} }& $\alpha\in\mathcal{A}$\\
\abs{\mathcal{L}_{l,\tau}}
\end{numcases}
% subsection controlling_rules (end)

>>>>

\subsubsection{Master plan} % (fold)
\label{ssub:master_plam}
With the cloud manufacturing platform operating, demander comes, signs up and publish orders, the structure of the order is depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations. Match module in platform informs the task messages to every matched resources and services. After the select decision makes by the demander, the selected resources and services prepare to the performance of the task.
Providers find frequent task after a bunch of successful accomplishment via resource reviews, then another type of job, service-call generated by them to gather certain type and amount of resources registered in the platform to create service in order to perform the certain task more efficient than before. Most of resource related decision making are well controlled by platform with the review module.

@@

Specifically, a simple instance with configuration \autoref{tab:simpleresourceconfiguration}--\ref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple resource configuration}
    \begin{tabular}{ccc}
    \toprule
    Resource & Type  & Capacity \\
    \midrule
    $r_1$ & 1     & 10 \\
    $r_2$ & 2     & 10 \\
    $r_3$ & 3     & 10 \\
    $r_4$ & 3     & 10 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simpleresourceconfiguration}%
\end{table}%
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
    $t_5$ & 1 & 0 & 3 & 2 & 3\\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources}
	\label{fig:scheduleChart}
\end{figure}
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period. Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.

@@

resources are renewable

\begin{table}[htbp]
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required and provided by $sc_l$ and $ms_l$ respectively, $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

@@

\begin{asparaenum}
\item Response for the task need $t_{ij}$($\tau\ge r_i$) with resource $mr_k$
\suspend{asparaenum}
\begin{subnumcases}{}
A_{k,\tau} \ge q_{\alpha,ij} &\\
P(mr_k) = \alpha & 
\end{subnumcases}
If $mr_k$ meets the above condition, provider of it will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$. If $mr_k$ was finally chose, available of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$. The available will be return back after the finish of $t_{ij}$.
\resume{asparaenum}
\item Response for the service-call need $sc_l$($\tau\ge r_l$) with resume $mr_k$
\suspend{asparaenum}
\begin{subnumcases}{}
C_{k,\tau} > 0 & \\
P(mr_k) = \alpha
\end{subnumcases}
If $mr_k$ meets the above condition, provider($p_a$) of it will response the service-call need, the provider($p_b$) of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$, it's possible to let $p_a=p_b$. If $mr_k$ was finally chose, capacity of $mr_k$ will change as:
\begin{subnumcases}{}
C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\\
C_{k,\tau} := 0 & otherwise
\end{subnumcases}

Capacity will not return back to $mr_k$ until the corresponding service $ms_l$ was repealed. Decision making of provider $p_b$ likes the one of demander's, but the final decision $\bm{mr}_l$ and $\bm{q}_l$ don't have to meet $\abs{\bm{mr}_l} = \abs{\mathcal{A}_{ij}}$, because different resource with the same type can gather together to bundle into one service, the only condition in need is that
\begin{subnumcases}{}
\sum_{k\in\mathcal{R}_{\alpha,\tau}} q_{\alpha,k} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{l,\tau}, P(mr) = \alpha \right\} & $\forall\alpha\in\mathcal{A}_l$
\end{subnumcases}
\resume{asparaenum}
\item Response for the task need $t_{ij}$($\tau\ge r_i$) with service $ms_l$.
\end{asparaenum}
Service is a combination contract among the participated resources and it's made oriented to the certain task, so the only condition for $ms_l$ to response $t_{ij}$ is:
\begin{subnumcases}{}
q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{B}_l$\\
\mathcal{A}_{ij} = \mathcal{B}_l
\end{subnumcases}

This condition is much same as service-call need $sc_l$ after the accomplishment frequent task $t_{ij}$:
\begin{subnumcases}{}
q_{\alpha,ij} = q_{\alpha,l} & $\forall\alpha\in\mathcal{A}_l$\\
\mathcal{A}_{ij} = \mathcal{A}_l
\end{subnumcases}
% subsection interactions_and_decisions (end)

@@

With the select decision of $t_{ij}$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
\begin{equation}
	\mathcal{P}_{ij} := \mathcal{P}_{ij}\cup \left\{ sc| sc\in\mathcal{L}_{k,\tau},sc \text{ is service-call} \right\} \cup \mathcal{G}_{k,\tau}
\end{equation}
Then, the provider will add $t_{ij}$ to queue or process buffer according to:
\begin{subnumcases}{}
\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \\
\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
\end{subnumcases}

@@

With the select decision of $sc_l$ to assign on $mr_k$ at $\tau$, the first thing for the provider of $mr_k$ is to set the predecessor set:
\begin{equation}
	\mathcal{P}_l := \mathcal{P}_l\cup \mathcal{L}_{k,\tau} \cup \mathcal{G}_{k,\tau}
\end{equation}
Then, the provider will add $sc_l$ to queue or process buffer according to:
\begin{subnumcases}{}
\mathcal{G}_{k,\tau} := \mathcal{G}_{k,\tau} \cup \{sc_l\} & if $\abs{\mathcal{L}_{k,\tau}\cup\mathcal{G}_{k,\tau}}=0$ \\
\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
\end{subnumcases}

@@

\begin{equation}
\min_{\forall\bm{f}^{(s)}}\left( \max_{j\in L^{(s)}}\left\{ f_j^{(s)} - r_j - p_j \right\} \right)
\end{equation}
\begin{numcases}{\text{s.t.}}
L^{(s)} = \left\{j| t_{j}\in \mathcal{L}^{(s)}_{k,\tau_0}\right\} & \\
f^{(s)}_h \le f_j^{(s)} - p_j & $h\in\mathcal{P}_j$,$j\in L^{(s)}$\\
G^{(s)} = \left\{j' | t_{j'}\in \mathcal{G}_{k,\tau_0}\right\} & \\
f^{(s)}_j =  \tau_0 + re_j & $j\in G^{(s)}$ \\
\sum_{j\in\left\{  j' |t_{j'} \in\mathcal{G}_{k,\tau}\right\}} q_j \le A_{k,\tau}& $\tau \ge \tau_0$ \label{eq:caplimitwithtime} \\
f^{(s)}_j \ge \tau_0 + p_j & $j\in L^{(s)}$
\end{numcases}

Like the RCPSP.
Since \autoref{eq:caplimitwithtime} is a time dependent function the schedule model cannot be
solved with mixed integer programming (MIP) techniques. In order to solve
the RCPSP with MIP{solvers such as CPLEX (cf. Bixby 1996), one has to
employ the 0{1 problem formulation of Pritsker et al. (1969).}}

@@

We will ignore resource type subscript $\alpha$ here for the reason that resources perform the task already meet the type needs. With the assumption given above, higher resource occupation($p_{ij}\cdot q_{ij}$), lower delay($f_{ij} - p_{ij} - r_{ij}$), larger difference between actual and expected product quality($\delta_{ij}-\gamma_{ij}$), will turn out higher rank value($rank$) changing:
\begin{subnumcases}{}
rank := rank +
\frac{\left( p_{ij}\cdot q_{ij} \right) \left( \delta_{ij}-\gamma_{ij} \right)}{e^{\left(f_{ij} - p_{ij} -r_{ij}\right)}} & $k\in\bm{k}$\\
\delta_{ij} = \min_{k\in\bm{k}}\left\{ \delta_k \right\} &\\
\delta_k \sim \mathcal{N}\left(\mu_k,\sigma_k^2 \right) & $k\in\bm{k}$
\end{subnumcases}

@@

This decision making is a control method for platform to keep the performance of tasks with content quality and efficiency. We denote the list of all resources with type $\alpha$ as $\bm{mr}_\alpha$ and the list of all services as $\bm{ms}$ at time $\tau$, after the sort these lists according to the scarcity and quality, the unqualified resources and services. Scarcity can be defined as:
\begin{subnumcases}{}
\sum_{k\in\{k|mr_k\in\bm{mr}_\alpha\}}\abs{\mathcal{L}_{k,\tau} } & $\alpha\in\mathcal{A}$ \label{eq:resourcescarcity}\\ 
\abs{\mathcal{L}_{l,\tau}} \label{eq:servicescarcity}
\end{subnumcases}

The scarcity of one service can be calculated with \autoref{eq:servicescarcity} while the scarcity of one type of resource can be calculated with \autoref{eq:resourcescarcity}.
% subsection controlling_rules (end)

### 2016-08-25 result.tex
阶段性定框架
添加新条目
re arrange
rearrange the paper structure
start to design 6 experiments

% !TEX root = Eco-Model.tex
\section{Numerical Results} % (fold)
\label{sec:numerical_results}

\subsection{effect of 1} % (fold)
\label{sub:effect_of_1}

% subsection effect_of_1 (end)

\subsection{effect of 2} % (fold)
\label{sub:effect_of_2}

% subsection effect_of_2 (end)

% xxx

% section numerical_results (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Experiment and result Analysis} % (fold)
\label{sec:Experiment_results}

Entities in the manufacturing ecosystem we designed above have these traits, they are: \begin{inparaenum}
\item autonomous and self-directed, 
\item social, interacting with other entities, 
\item controlled by the environment, 
\item self-contained.
\end{inparaenum} They optimize their multi-objective decision makings to interact with others and the environment, hence, agent-based modeling and simulation(ABMS) technique\cite{Macal2009,north2007managing} is suitable for the study of the complex system. With the help of Repast Simphony\cite{North2013} package, we realized the ecosystem model and performed some experiments on it.
\subsection{Agent-based modeling and simulation design} % (fold)
\label{sub:agent_based_modeling_and_simulation}
\subsubsection{Model realization}
% \begin{asparaenum}
% \item Platform
% \suspend{asparaenum}
\begin{figure}[htbp]
	\centering
	\tiny
	\begin{tikzpicture}
	\input{figures/cCloudPlatform}
	\end{tikzpicture}
	\caption{Cloud Platform}
	\label{fig:platform}
\end{figure}
% \resume{asparaenum}
% \item User related
% \suspend{asparaenum}
\begin{figure}[htbp]
    \centering
    \tiny
    \begin{tikzpicture}
    \input{figures/cUser}
    \input{figures/cProvider}
\input{figures/cDemander}
    \end{tikzpicture}
    \caption{User related classes}
    \label{fig:userclassed}
\end{figure}
% \resume{asparaenum}
% \item Job related
% \suspend{asparaenum}
\begin{figure}[htbp]
    \centering
    \tiny
    \begin{tikzpicture}
    \input{figures/cJob}
    \input{figures/cTask}
    \input{figures/cServiceCall}
    \end{tikzpicture}
    \caption{Job related classes}
    \label{fig:jobclassed}
\end{figure}
% \resume{asparaenum}
% \item Machine related
% \end{asparaenum}
\begin{figure}[htbp]
    \centering
    \tiny
    \begin{tikzpicture}
    \input{figures/cMachine}
    \input{figures/cResource}
    \input{figures/cService}
    \end{tikzpicture}
    \caption{Machine related classes}
    \label{fig:machineclassed}
\end{figure}

\subsubsection{Behavior interfaces and classes}
% \begin{asparaenum}
% \item Assign behavior
% \suspend{asparaenum}
\begin{figure}[htbp]
    \centering
    \tiny
    \begin{tikzpicture}
    \input{figures/iAssignBehavior}
    \input{figures/iSelectBehavior}
    \input{figures/iResponseBehavior}
    \input{figures/iProcessBehavior}
    \input{figures/iReleaseBehavior}
    % \input{figures/cServiceAssign}
    % \input{figures/cResourceAssign}
    \end{tikzpicture}
    \caption{Assign interface and related classes}
    \label{fig:assigninterface}
\end{figure}

% \resume{asparaenum}
% \item Process behavior
% \suspend{asparaenum}

% \begin{figure}[htbp]
%     \centering
%     \scriptsize
%     \begin{tikzpicture}
%     \input{figures/iProcessBehavior}
%     \input{figures/cProcessInTask}
%     \input{figures/cProcessInServiceCall}
%     \end{tikzpicture}
%     \caption{Process interface and related classes}
%     \label{fig:processinterface}
% \end{figure}
% \resume{asparaenum}
% \item Release behavior
% \suspend{asparaenum}

% \begin{figure}[htbp]
%     \centering
%     \scriptsize
%     \begin{tikzpicture}
%     \input{figures/iReleaseBehavior}
%     \input{figures/cResourceRelease}
%     \input{figures/cServiceRelease}
%     \end{tikzpicture}
%     \caption{Release interface and related classes}
%     \label{fig:releaseinterface}
% \end{figure}
% \resume{asparaenum}
% \item Response behavior
% \suspend{asparaenum}

% \begin{figure}[htbp]
%     \centering
%     \scriptsize
%     \begin{tikzpicture}
%     \input{figures/iResponseBehavior}
%     \input{figures/cResourceResponse}
%     \input{figures/cServiceResponse}
%     \end{tikzpicture}
%     \caption{Response interface and related classes}
%     \label{fig:reponseinterface}
% \end{figure}
% \resume{asparaenum}
% \item Select behavior
% \end{asparaenum}

% \begin{figure}[htbp]
%     \centering
%     \scriptsize
%     \begin{tikzpicture}
%     \input{figures/iSelectBehavior}
%     \input{figures/cSelectInTask}
%     \input{figures/cSelectInServiceCall}
%     \end{tikzpicture}
%     \caption{Select interface and related classes}
%     \label{fig:selectinterface}
% \end{figure}

\subsection{Experiments} % (fold)
\label{ssub:case_design}
We use the RanGen\cite{Demeulemeester2003,Vanhoucke2008} to generate the order data in the well-known Patterson format with the parameters setting listed in tab..., the control parameters are .... we design these experiments to validate service-incubate mode, outsource mode and metabolism mode \autoref{tab:grouping}

\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Experiments grouping}
    \begin{tabular}{llcc}
    \toprule
          &       & With metabolism & Without metabolism \\
    \midrule
    \multicolumn{1}{l}{\multirow{2}[0]{*}{Service-incubate}} & with outsource & Exp. 11 &Exp. 12 \\\cline{2-4}
    \multicolumn{1}{l}{} & without outsource & Exp. 21 & Exp. 22 \\\hline
    \multicolumn{2}{l}{Resource-only} & Exp. 31 & Exp. 32 \\
    \bottomrule
    \end{tabular}%
  \label{tab:grouping}%
\end{table}%

% subsubsection case_design (end)

\subsubsection{Parameters setting} % (fold)
\label{ssub:parameters_setting}
All the following experiments are simulated with same random seed to make no difference on the coming of order, provider and other irrelevant configuration to our validation.
% subsubsection parameters_setting (end)

\subsubsection{Result and analysis} % (fold)
\label{ssub:result_and_analysis}

% subsubsection result_and_analysis (end)
